Sexual selection improves population fitness: a meta-analysis

### 2018-08-09 meta_analysis_sexual_selection_pop_fitness.Rmd
July Update 3
Remove rownames Table S6

fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
```

>>>>

fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% `row.names<-`(NULL) %>% pander(split.cell = 40, split.table = Inf, digits = 2)
```
